ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-11-01 proposal.tex
Updated labNotebook.tex and proposal.tex

Introduction to system identification...., Mathworks' MATLAB has the system
identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.

@@

\subsection{Example 2: ..........}
\label{sec:sysID-Example2}

@@

% \vspace*{12pt}
% \noindent
% One such method that has been utilized to make a cart follow a customer through a store is a mobile platform interface that implements ultrasound and radio transmissions technology~\cite{Sales2016-CompaRob}. Another method that has been implemented is the use of a GRU (Gated Recurrent Unit) network to detect shopping habits of customers while also using a LiDAR (Light Detection and Ranging) sensor and camera to detect and map the customer using a two-dimensional skeleton and follow them through the store~\cite{islam_lam_fukuda_kobayashi_kuno_2019}. Therein, authors utilized an Arduino MEGA 2560, six ultrasonic sensors, two DC motors with PWM (Pulse Width Modulation), an Android Studio IDE device, and Bluetooth for detecting a customer and following them through the store~\cite{Rawashdeh2017-Person}.

% \vspace*{12pt}
% \noindent
% In the current project, we are implementing XBee S2C RF radios, which are inexpensive and easily configurable, as a remote target device that is carried by the user. The robot will be able to track this remote instead of using line of sight methods~\cite{Miah2018-Intelligent}. In addition to the XBee S2C RF radios, we will equip the robot with a parabolic reflector, which improves Wi-Fi reception at various distances and angles, \textit{i.e.,} angle of arrivals of RF signals from the remote, based on research done previously in this type of robot localization and mapping~\cite{Miah2018-Intelligent}~\cite{Li2013ANA}.

% \vspace*{12pt}
% \noindent
% The approach using signal strength of RF signals also requires an understanding of multipath interference which is common in Wi-Fi based wireless positioning sensing systems. Authors in~\cite{xie_jiang_zhao_zhang_2019} explain that using course estimation calculations such as received signal strength indicator (RSSI) and time difference of arrival (TDoA) is key to compensate for the multipath interference in received signals. The work in ~\cite{ladd_bekris_rudys_kavraki_wallach_2005} shows a different approach to the multipath issue by using an IEEE 802.11b wireless ethernet device to measure RF signals. This device system was used because it is communicable between a mobile device and a localization based service with low complexity for the user. Also, in~\cite{lindhe_johansson_bicchi_2007}, the research states several other ways to counteract the multipath fading with methods such as antenna diversity, frequency spreading, or adaptive antenna arrays. The method used in this paper was to sample the radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position in an indoor environment. Lastly, in~\cite{Lindhe2009} the method that is utilized exploits multipath fading by measuring the signal-to-noise ratio (SNR) and adjusting the robot's motion to spend more time where the channel strength is greater.

% \vspace*{12pt}
% \noindent
% All of the solutions that were found required direct line-of-sight between the robot and the user. In this project we aim to use the XBee S2C RF radios and a parabolic reflector combined into a rotating system similar to the one presented in~\cite{Miah2018-Intelligent} in order to have the robot track the customer through a store without using line-of-sight sensing. The major challenge of this implementation will be estimating the distance between the robot and the remote in varying environments.

@@

% \section{System Architecture}
% The overall system architecture of this project consists of two subsystems which are the Mobile Cart and the Remote Target (user or customer, for example) as shown in \autoref{fig:sys_block_diag}. The proposed mobile cart is a wheeled robot that sends and receives radio signals to follow the remote target. The remote acts as the target for the mobile cart system by sending radio signals back and forth with the cart.

@@

% \subsection{System Components}
% There are several components that are required for the mobile cart system. Although some of these parts are available in the Bradley University laboratory, other parts must be purchased. The parts that exist in the lab are shown in \autoref{tab:Partslablist}. Also, \autoref{tab:Partslist} shows the list of parts that we must purchase. The parts lists shown are the parts needed to build two mobile cart systems.

% \begin{table}[h!]
%   \centering
%   \begin{tabular}{c|c}
%       \toprule
%       \textbf{Quantity} & \textbf{Parts}\\
%       \toprule
%       2 & Budget Bot Chassis\\
%       4 & 10 uF Ceramic Capacitor\\
%       4 & LM1117 Regulator\\
%       2 & Battery Packs for Budget Bot\\
%       8 & 9V Batteries\\
%       4 & Solderable PCB Boards\\
%       3 & XBee USB Adapter\\
%       \bottomrule
%       %\multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
%       %\bottomrule
%   \end{tabular}
%   \caption{Parts Available in Laboratory}
%   \label{tab:Partslablist}
% \end{table}

% \begin{table}[h!]
%   \centering
%   \begin{tabular}{c|c|c}
%     \toprule
%     \textbf{Quantity} & \textbf{Parts} & \textbf{Price}\\
%     \toprule
%     4 & Pololu 37D Metal Gear motor 4751 & \$ 39.95\\
%     12 & XBee S2C Module & \$ 23.10\\
%     10 & XBee Adapter Board & \$ 4.99\\
%     2 & Twotrees 4 Lead Nema 17 Stepper Motor & \$ 9.99\\
%     1 & 4-Pin JST SH Connector - 20 Pack & \$ 7.99\\
%     1 & 6-Pin JST SH Connector - 10 Pack & \$ 9.99\\
%     1 & Aluminum Foil Tape - 2 in x 5 yd & \$ 6.05\\
%     \bottomrule
%     \multicolumn{2}{r|}{\textbf{Total}} & \$ 562.34\\
%     \bottomrule
%   \end{tabular}
%   \caption{Purchased parts for the Robotic Cart Project}
%   \label{tab:Partslist}
% \end{table}

% \vspace*{12pt}
% \noindent
% The main components for this project are the Budget Bot Chassis (\autoref{fig:budgetBotChassis}), the BeagleBone Blue embedded computer (\autoref{fig:beagleboneBlue}), and the XBee S2C Modules (\autoref{fig:XBeeModule}). Another major component is the reflector array that
% will be used to directionalize the RF signals received from the remote target that is with the user.

% \begin{figure}
%   \centering
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/budgetbot_chassis}
%     \captionsetup{width=\textwidth}
%     \caption{Budget Bot Chassis}
%     \label{fig:budgetBotChassis}
%   \end{minipage}%
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/beaglebone_blue}
%     \captionsetup{width=\textwidth}
%     \caption{BeagleBone Blue}
%     \label{fig:beagleboneBlue}
%   \end{minipage}
%   \begin{minipage}[t]{0.32\textwidth}
%     % \includegraphics[width=1\textwidth]{figs/img/Xbee-S2C-Module}
%     \captionsetup{width=\textwidth}
%     \caption{XBee S2C Module}
%     \label{fig:XBeeModule}
%   \end{minipage}
% \end{figure}

% \vspace*{12pt}
% \noindent
% The reflector array will be mounted on top of the cart where it will be attached with a stepper motor. There are two reflector designs that we will be evaluating in this project. The first, shown in \autoref{fig:parabolodialReflector}, is a paraboloidal reflector which maximizes the signal strength of signals that come into the reflector directly perpendicularly. Since the remote will be carried by the user, it is likely that it will be positioned at a higher altitude than the reflector array. The paraboloidal reflector design may not be able to pick up the signals from the remote as well because of this. To solve this problem, we designed a combination parabolic/paraboloidal reflector, as shown in \autoref{fig:parabolicReflector}. The lower half of this reflector is paraboloidal in shape to limit the signals coming from below. The upper part of the reflector is strictly parabolic. This shape focuses the signals in the horizontal plane, but allows signals from above to still be received. We plan to construct both of these reflector designs by 3d printing the frames, then lining them with reflective foil tape. Both models will then be tested to determine which design works better.

% \begin{figure}[h!]
%   \centering
%   \begin{minipage}[t]{0.5\textwidth}
%     \centering
%     % \includegraphics[height=2in]{figs/img/paraboloidalReflector}
%     \captionsetup{width=\textwidth, justification=raggedright}
%     \caption{Paraboloidal Reflector Model}
%     \label{fig:parabolodialReflector}
%   \end{minipage}
%   \begin{minipage}[t]{0.4\textwidth}
%     \centering
%     % \includegraphics[height=2in]{figs/img/parabolicReflector}
%     \captionsetup{width=\textwidth, justification=raggedright}
%     \caption{Combined Parabolic/Paraboloidal Reflector}
%     \label{fig:parabolicReflector}
%   \end{minipage}
% \end{figure}

@@

% \subsection{Algorithms}
% As mentioned previously, there are two steps in the operation of the system. These steps are the localization of the remote and the navigation of the robot. This section describes the algorithms used for these tasks.

% \subsubsection{Localization Algorithm}
% The strength of the radio signals between the cart and remote will be used to estimate the position of the remote relative to the cart. By rotating the sensor array 90 degrees and measuring the signal strength of messages from the remote at several steps in the rotation, the bearing of the remote can be estimated as the direction in which the maximum signal strength is received. To estimate the distance between the cart and the remote, the signal strength will be measured and used to calculate the distance. The omnidirectional radio module on top will be responsible for coordinating the messages from the remote by sending the remote commands that tell the remote when to send signals. A flowchart of the localization algorithm is shown in \autoref{fig:locAlgoFlowchart}. Also, a pseudo-code version of the algorithm is shown in \autoref{alg:locAlgo}

% \begin{figure}
%   \centering
%   \input{figs/dia/localizationAlgoFlowchart.tex}
%   \caption{Flowchart of Localization Algorithm}
%   \label{fig:locAlgoFlowchart}
% \end{figure}

% \begin{algorithm}[h!]
%   \SetAlgoLined
%   \KwOut{Range $d_{ref}$ and Bearing $\theta_{ref}$ of remote}
%   Constants: step angle $\theta_{step}$\\
%   Static direction variable $dir = 1$
%   \Begin
%   {
%     \uIf{Reflectors not rotated 90\textdegree}
%     {
%       Send signal strength request to remote\\
%       Get signal strengths from receivers\\
%       Rotate reflectors through an angle of $dir*\theta_{step}$\\
%     }
%     \Else
%     {
%       $\theta_{ref} =$ direction of max signal strength\\
%       Compute $d_{ref}$ using signal strength\\
%       $dir = -dir$\\
%     }
%   }
%   \caption{Localization Algorithm}
%   \label{alg:locAlgo}
% \end{algorithm}

% \subsubsection{Navigation Algorithm}
% Once the bearing and distance of the remote are estimated, the cart must move to follow the remote. We will use a modified Point Navigation algorithm to navigate the robot to follow the remote. The robot will estimate the coordinates of the remote with respect to the robot's local reference frame. The robot will then apply actuation to move to the point that is a set following distance from the remote. A flowchart of the navigation algorithm is shown in \autoref{fig:navAlgoFlowchart}. Also, a pseudo-code version of the algorithm is shown in \autoref{alg:navAlgo}.

% \begin{figure}
%   \centering
%   \input{figs/dia/navigationAlgoFlowchart.tex}
%   \caption{Flowchart of Navigation Algorithm}
%   \label{fig:navAlgoFlowchart}
% \end{figure}

% \begin{algorithm}[h!]
%   \SetAlgoLined
%   \KwIn{Range $d_{ref}$ and Bearing $\theta_{ref}$ of Remote}
%   \KwOut{Mobile Robot Trajectory}
%   Constants: following distance $d_f$ and proportional gains $K_p$ and $K_\omega$\\
%   \Begin
%   {
%     Compute target point with respect to robot's local frame as $x_{ref} = (d_{ref} - d_f)\cos \theta_{ref}$, $y_{ref} = (d_{ref} - d_f)\sin \theta_{ref}$\\
%     Compute linear speed $v(t) = sign(x_{ref})K_p\sqrt{x_{ref}^2 + y_{ref}^2}$\\
%     Compute $\omega(t) = K_\omega \theta_{ref}$\\
%     Apply wheel speeds to robot\\
%   }
%   \caption{Navigation Algorithm}
%   \label{alg:navAlgo}
% \end{algorithm}

@@

\section{Concluding Remarks}
Autonomous vehicles have a numerous amount of useful applications in today's society. ...

>>>>

System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system. There are many components or systems that engineers use to accomplish a task that they are assigned without knowing the exact behavior of this system for a given input. Without knowing the response of this black-box, there could be unexpected consequences from a system. The goal of the system identification methodology is to get an accurate estimation of the system response to any given input. Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.

@@

\subsection{Example 2: Selecting Model Structures for Multivariable Systems}
\label{sec:sysID-Example2}
This example discusses solutions for modeling both MISO and MIMO models using Mathworks' Matlab System Identification Toolbox. As the article discusses, MISO system models are easier to develop because all model structures used by the toolbox support models with a single output and multiple inputs. Therefore, the process for developing a model for a MISO system is importing the data as an iddata object, removing the mean from the data, and estimating the solution using any model structure available in the toolbox. The command line can be used by using the function associated with the model structure name and then using the compare function to get the best fit percentage. For MIMO systems, there are not model structures built into the System Identification Toolbox and they must be imported instead. Otherwise the process is very similar to that of a MISO system. For a MIMO system, using the compare function can be crucial. The compare function will tell which output channel is the most difficult to develop a model for, if it is possible at all. With this information, the output channel that is hardest to model should first be modeled individually because there will be less freedom in what model structures are available. The other channels should be able to closely relate to the model for the output channel you selected.

@@

@@

\section{System Architecture}
The overall system architecture of this project consists of six subsystems which are the steering, acceleration, brake, speed, shift, and cruise control systems as shown in \autoref{fig:sys_block_diag}.

@@

@@

@@

\section{Concluding Remarks}
Autonomous vehicles have a numerous amount of useful applications in today's society. From being used for delivering packages to allowing drivers to rest while traveling, as the technology for autonomous vehicles is enhanced, they will become an enticing product that many consumers will purchase and use. One of the biggest concerns with autonomous vehicles today is the risk associated with public safety. One solution to reducing the safety risk is ensuring that accurate controllers are developed to reliably control each subsystem involved with the controlling the movement of the autonomous vehicle. Due to non-linear behaviors, there is no simple solution for developing reliable controllers. This project will focus on deriving models of some main subsystems so that these non-linear behaviors are removed and smooth controllers can be developed.
